\LARGE \bf IMU-based pose-estimation for spherical robots with limited resources

### 2021-05-31 mfi21/ieeeconf/root.tex
changed position of picture and therefore text. Added caption

This paper introduces an IMU-based orientation and position algorithm for spherical robots with limited computational power and the need for real-time estimations.
Also, the algorithm does not rely on one specific locomotion approach, but it assumes a rotation of the IMU together with at least the shell of the robot, if not the whole robot.

@@

>>>>

This paper introduces an IMU-based orientation and position algorithm for spherical robots with limited computational power and the need for real-time estimations.
Also, the algorithm does not rely on one specific locomotion approach, but it assumes a rotation of the IMU together with at least the shell of the robot, if not the whole robot. 
Such as the prototype developed at the computer science chair VII of the University of Wuerzburg,  depicted in Figure \ref{fig:prototype}, which is inspired by previous work such as Daedalus \cite{rossi2021daedalus}.
The evaluations made in this paper were done with the setup of the IMUs of this prototype.
The Livox Mid-100 was used as laser scanner.
Due to the lack of a locomotion system, the sphere needs to be rolled externally. 
The evaluation will also show and discuss the resulting point clouds of this prototype with the presented pose estimation.
\begin{figure}[b]
\includegraphics[width=0.484\linewidth]{./graphics/photoReal1.jpeg}
\includegraphics[width=0.50\linewidth]{./graphics/photoReal2.jpeg}
\caption{Prototype to test the algorithm in an envisaged technical environment. The main payload is the Livox Mid-100 laser-scanner. For pose-estimation, three IMUs of the manufacturer Phidget are placed on the middle plate and a Raspberry Pi 4 for the calculations. On the top are two batteries, and on the bottom one voltage stabilizer and breakout box of the laser-scanner. }
\label{fig:prototype}
\end{figure}

@@

%TODO Fabian, put input of laserscanns here
